---
title: "Fusion Weights Analysis"
author: "sheng Qian"
date: "2023-4-20"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---


```{r echo=FALSE}
get_rsq <- function(path){
  lst = read.table(path,as.is=T)[,1]
  names = gsub(".wgt.RDat","",basename(lst))
  N = length(lst)
  cv_rsq <- data.frame(matrix(ncol = 2, nrow = 0))
  colnames(cv_rsq) <- c("top1","enet")
  
  for ( i in 1:N ) {
    load(paste0("/project2/xinhe/shengqian/fusion_twas-master/",lst[i]))
    g.method <- "enet"
    if (exists("cv.performance")){
      if (!(g.method %in% names(cv.performance[1,]))){
        next
      }
    }
    wgt.matrix <- wgt.matrix[abs(wgt.matrix[, g.method]) > 
                             0, , drop = F]
    wgt.matrix <- wgt.matrix[complete.cases(wgt.matrix), 
                           , drop = F]
  
    if (nrow(wgt.matrix) == 0) 
      next
  
    cv_rsq <- rbind(cv_rsq,cv.performance[1,2:3])
  }
  colnames(cv_rsq) <- c("top1","enet")
  cv_rsq <- na.omit(cv_rsq)
}
```

```{r echo=FALSE}
wholeblood_3kb <- get_rsq("/project2/xinhe/shengqian/fusion_twas-master/methylation_wholeblood_3kb_tmp.pos")
wholeblood_100kb <- get_rsq("/project2/xinhe/shengqian/fusion_twas-master/methylation_wholeblood_tmp.pos")
wholeblood_500kb <- get_rsq("/project2/xinhe/shengqian/fusion_twas-master/methylation_wholeblood_500kb_tmp.pos")

prostate_3kb <- get_rsq("/project2/xinhe/shengqian/fusion_twas-master/methylation_prostate_3kb_tmp.pos")
prostate_100kb <- get_rsq("/project2/xinhe/shengqian/fusion_twas-master/methylation_prostate_tmp.pos")
prostate_500kb <- get_rsq("/project2/xinhe/shengqian/fusion_twas-master/methylation_prostate_500kb_tmp.pos")

lung_3kb <- get_rsq("/project2/xinhe/shengqian/fusion_twas-master/methylation_lung_3kb_tmp.pos")
lung_100kb <- get_rsq("/project2/xinhe/shengqian/fusion_twas-master/methylation_lung_tmp.pos")
lung_500kb <- get_rsq("/project2/xinhe/shengqian/fusion_twas-master/methylation_lung_500kb_tmp.pos")
```

To understand how distance affects FUSION model performance, I sampled 10% CpGs on each chromosome and extended to +/- 3kb, 100kb, 500kb. Then I ran FUSION with heritability cutoff 0.01. The plots from left to right are 3kb, 100kb, 500kb. Enet and top1 have similar rsq. Wholeblood and Prostate models are best at 3kb, lung model is best at 100kb


## Fusion model of WholeBlood DNA methylation (smaple size 47). 

```{r,fig.width=9,fig.height=3,echo=FALSE}
par(mfrow=c(1,3)) 
plot(wholeblood_3kb$top1,wholeblood_3kb$enet,pch=16,cex=0.2,xlab = "top1 rsq",ylab = "enet rsq", main = paste0("enet rsq:",round(mean(wholeblood_3kb$enet),3)," top1 rsq: ",round(mean(wholeblood_3kb$top1),3)))
plot(wholeblood_100kb$top1,wholeblood_100kb$enet,pch=16,cex=0.2,xlab = "top1 rsq",ylab = "enet rsq", main = paste0("enet rsq:",round(mean(wholeblood_100kb$enet),3)," top1 rsq: ",round(mean(wholeblood_100kb$top1),3)))
plot(wholeblood_500kb$top1,wholeblood_500kb$enet,pch=16,cex=0.2,xlab = "top1 rsq",ylab = "enet rsq", main = paste0("enet rsq:",round(mean(wholeblood_500kb$enet),3)," top1 rsq: ",round(mean(wholeblood_500kb$top1),3)))
```

## Fusion model of Prostate DNA methylation (smaple size 123).

```{r,fig.width=9,fig.height=3,echo=FALSE}
par(mfrow=c(1,3)) 
plot(prostate_3kb$top1,prostate_3kb$enet,pch=16,cex=0.2,xlab = "top1 rsq",ylab = "enet rsq", main = paste0("enet rsq:",round(mean(prostate_3kb$enet),3)," top1 rsq: ",round(mean(prostate_3kb$top1),3)))
plot(prostate_100kb$top1,prostate_100kb$enet,pch=16,cex=0.2,xlab = "top1 rsq",ylab = "enet rsq", main = paste0("enet rsq:",round(mean(prostate_100kb$enet),3)," top1 rsq: ",round(mean(prostate_100kb$top1),3)))
plot(lung_500kb$top1,lung_500kb$enet,pch=16,cex=0.2,xlab = "top1 rsq",ylab = "enet rsq", main = paste0("enet rsq:",round(mean(lung_500kb$enet),3)," top1 rsq: ",round(mean(lung_500kb$top1),3)))
```

## Fusion model of Lung DNA methylation (smaple size 223).

```{r,fig.width=9,fig.height=3,echo=FALSE}
par(mfrow=c(1,3)) 
plot(lung_3kb$top1,lung_3kb$enet,pch=16,cex=0.2,xlab = "top1 rsq",ylab = "enet rsq", main = paste0("enet rsq:",round(mean(lung_3kb$enet),3)," top1 rsq: ",round(mean(lung_3kb$top1),3)))
plot(lung_100kb$top1,lung_100kb$enet,pch=16,cex=0.2,xlab = "top1 rsq",ylab = "enet rsq", main = paste0("enet rsq:",round(mean(lung_100kb$enet),3)," top1 rsq: ",round(mean(lung_100kb$top1),3)))
plot(lung_500kb$top1,lung_500kb$enet,pch=16,cex=0.2,xlab = "top1 rsq",ylab = "enet rsq", main = paste0("enet rsq:",round(mean(lung_500kb$enet),3)," top1 rsq: ",round(mean(lung_500kb$top1),3)))
```