---
title: "SCZ - Brain Cortex"
author: "sheng Qian"
date: "2021-2-6"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
params:
  analysis_id: "SCZ_Brain_Cortex"
  trait_id: "SCZ_2018"
  weight: "Brain_Cortex"
---

```{r echo=F}
trait_id <- "SCZ_2018"
trait_name <- "SCZ"
source("/project2/xinhe/shengqian/cTWAS/cTWAS_analysis/code/ctwas_config_b38.R")

trait_dir <- paste0("/project2/xinhe/shengqian/cTWAS/cTWAS_analysis/data/", trait_id)
results_dirs <- list.dirs(trait_dir, recursive=F)

options(digits = 4)
```

## Load cTWAS results for all weights

```{r echo=F}
# df <- list()
# 
# for (i in 1:length(results_dirs)){
#   print(i)
#   results_dir <- results_dirs[i]
#   weight <- rev(unlist(strsplit(results_dir, "/")))[1]
#   analysis_id <- paste0("SCZ_",weight)
# 
#   #load ctwas results
#   ctwas_res <- data.table::fread(paste0(results_dir, "/", analysis_id, "_ctwas.susieIrss.txt"))
# 
#   #make unique identifier for regions and effects
#   ctwas_res$region_tag <- paste(ctwas_res$region_tag1, ctwas_res$region_tag2, sep="_")
#   ctwas_res$region_cs_tag <- paste(ctwas_res$region_tag, ctwas_res$cs_index, sep="_")
# 
#   #load z scores for SNPs and collect sample size
#   load(paste0(results_dir, "/", analysis_id, "_expr_z_snp.Rd"))
# 
#   sample_size <- z_snp$ss
#   sample_size <- as.numeric(names(which.max(table(sample_size))))
# 
#   #separate gene and SNP results
#   ctwas_gene_res <- ctwas_res[ctwas_res$type == "gene", ]
#   ctwas_gene_res <- data.frame(ctwas_gene_res)
#   ctwas_snp_res <- ctwas_res[ctwas_res$type == "SNP", ]
#   ctwas_snp_res <- data.frame(ctwas_snp_res)
# 
#   #add gene information to results
#   sqlite <- RSQLite::dbDriver("SQLite")
#   db = RSQLite::dbConnect(sqlite, paste0("/project2/compbio/predictdb/mashr_models/mashr_", weight, ".db"))
#   query <- function(...) RSQLite::dbGetQuery(db, ...)
#   gene_info <- query("select gene, genename, gene_type from extra")
#   RSQLite::dbDisconnect(db)
# 
#   ctwas_gene_res <- cbind(ctwas_gene_res, gene_info[sapply(ctwas_gene_res$id, match, gene_info$gene), c("genename", "gene_type")])
# 
#   #add z scores to results
#   load(paste0(results_dir, "/", analysis_id, "_expr_z_gene.Rd"))
#   ctwas_gene_res$z <- z_gene[ctwas_gene_res$id,]$z
# 
#   z_snp <- z_snp[z_snp$id %in% ctwas_snp_res$id,]
#   ctwas_snp_res$z <- z_snp$z[match(ctwas_snp_res$id, z_snp$id)]
# 
#   #merge gene and snp results with added information
#   ctwas_snp_res$genename=NA
#   ctwas_snp_res$gene_type=NA
# 
#   ctwas_res <- rbind(ctwas_gene_res, ctwas_snp_res[,colnames(ctwas_gene_res)])
# 
#   #get number of eQTL for genes
#   num_eqtl <- c()
#   for (i in 1:22){
#     load(paste0(results_dir, "/", analysis_id, "_expr_chr", i, ".exprqc.Rd"))
#     num_eqtl <- c(num_eqtl, unlist(lapply(wgtlist, nrow)))
#   }
#   ctwas_gene_res$num_eqtl <- num_eqtl[ctwas_gene_res$id]
# 
#   #get number of SNPs from s1 results; adjust for thin argument
#   ctwas_res_s1 <- data.table::fread(paste0(results_dir, "/", analysis_id, "_ctwas.s1.susieIrss.txt"))
#   n_snps <- sum(ctwas_res_s1$type=="SNP")/thin
#   rm(ctwas_res_s1)
# 
#   #load estimated parameters
#   load(paste0(results_dir, "/", analysis_id, "_ctwas.s2.susieIrssres.Rd"))
# 
#   #estimated group prior
#   estimated_group_prior <- group_prior_rec[,ncol(group_prior_rec)]
#   names(estimated_group_prior) <- c("gene", "snp")
#   estimated_group_prior["snp"] <- estimated_group_prior["snp"]*thin #adjust parameter to account for thin argument
# 
#   #estimated group prior variance
#   estimated_group_prior_var <- group_prior_var_rec[,ncol(group_prior_var_rec)]
#   names(estimated_group_prior_var) <- c("gene", "snp")
# 
#   #report group size
#   group_size <- c(nrow(ctwas_gene_res), n_snps)
# 
#   #estimated group PVE
#   estimated_group_pve <- estimated_group_prior_var*estimated_group_prior*group_size/sample_size
#   names(estimated_group_pve) <- c("gene", "snp")
# 
#   #ctwas genes using PIP>0.8
#   ctwas_genes_index <- ctwas_gene_res$susie_pip>0.8
#   ctwas_genes <- ctwas_gene_res$genename[ctwas_genes_index]
# 
#   #twas genes using bonferroni threshold
#   alpha <- 0.05
#   sig_thresh <- qnorm(1-(alpha/nrow(ctwas_gene_res)/2), lower=T)
# 
#   twas_genes_index <- abs(ctwas_gene_res$z) > sig_thresh
#   twas_genes <- ctwas_gene_res$genename[twas_genes_index]
# 
#   #gene PIPs and z scores
#   gene_pips <- ctwas_gene_res[,c("genename", "region_tag", "susie_pip", "z", "region_cs_tag", "num_eqtl")]
# 
#   #total PIPs by region
#   regions <- unique(ctwas_gene_res$region_tag)
#   region_pips <- data.frame(region=regions, stringsAsFactors=F)
#   region_pips$gene_pip <- sapply(regions, function(x){sum(ctwas_gene_res$susie_pip[ctwas_gene_res$region_tag==x])})
#   region_pips$snp_pip <- sapply(regions, function(x){sum(ctwas_snp_res$susie_pip[ctwas_snp_res$region_tag==x])})
#   region_pips$snp_maxz <- sapply(regions, function(x){max(abs(ctwas_snp_res$z[ctwas_snp_res$region_tag==x]))})
#   region_pips$which_snp_maxz <- sapply(regions, function(x){ctwas_snp_res_index <- ctwas_snp_res$region_tag==x; ctwas_snp_res$id[ctwas_snp_res_index][which.max(abs(ctwas_snp_res$z[ctwas_snp_res_index]))]})
# 
#   #total PIPs by causal set
#   regions_cs <- unique(ctwas_gene_res$region_cs_tag)
#   region_cs_pips <- data.frame(region_cs=regions_cs, stringsAsFactors=F)
#   region_cs_pips$gene_pip <- sapply(regions_cs, function(x){sum(ctwas_gene_res$susie_pip[ctwas_gene_res$region_cs_tag==x])})
#   region_cs_pips$snp_pip <- sapply(regions_cs, function(x){sum(ctwas_snp_res$susie_pip[ctwas_snp_res$region_cs_tag==x])})
# 
#   df[[weight]] <- list(prior=estimated_group_prior,
#                      prior_var=estimated_group_prior_var,
#                      pve=estimated_group_pve,
#                      ctwas=ctwas_genes,
#                      twas=twas_genes,
#                      gene_pips=gene_pips,
#                      region_pips=region_pips,
#                      sig_thresh=sig_thresh,
#                      region_cs_pips=region_cs_pips)
# }

#save(df, file=paste(trait_dir, "results_df.RData", sep="/"))
```

```{r echo=F}
load(paste(trait_dir, "results_df.RData", sep="/"))

output <- data.frame(weight=names(df),
                     prior_g=unlist(lapply(df, function(x){x$prior["gene"]})),
                     prior_s=unlist(lapply(df, function(x){x$prior["snp"]})),
                     prior_var_g=unlist(lapply(df, function(x){x$prior_var["gene"]})),
                     prior_var_s=unlist(lapply(df, function(x){x$prior_var["snp"]})),
                     pve_g=unlist(lapply(df, function(x){x$pve["gene"]})),
                     pve_s=unlist(lapply(df, function(x){x$pve["snp"]})),
                     n_ctwas=unlist(lapply(df, function(x){length(x$ctwas)})),
                     n_twas=unlist(lapply(df, function(x){length(x$twas)})),
                     row.names=NULL,
                     stringsAsFactors=F)
```


## Plot estimated prior parameters and PVE

```{r echo=F}

#plot estimated group prior

output <- output[order(-output$prior_g),]

par(mar=c(4.1, 4.1, 4.1, 2.1))

plot(output$prior_g, type="l", ylim=c(0, max(output$prior_g, output$prior_s)*1.1),
     xlab="", ylab="Estimated Group Prior", xaxt = "n", col="blue")
lines(output$prior_s)

axis(1, at = 1:nrow(output),
     labels = output$weight,
     las=2,
     cex.axis=0.6)

####################
#plot estimated group prior variance

par(mar=c(4.1, 4.1, 4.1, 2.1))

plot(output$prior_var_g, type="l", ylim=c(0, max(output$prior_var_g, output$prior_var_s)*1.1),
     xlab="", ylab="Estimated Group Prior Variance", xaxt = "n", col="blue")
lines(output$prior_var_s)

axis(1, at = 1:nrow(output),
     labels = output$weight,
     las=2,
     cex.axis=0.6)

####################
#plot PVE

output <- output[order(-output$pve_g),]

par(mar=c(4.1, 4.1, 4.1, 2.1))

plot(output$pve_g, type="l", ylim=c(0, max(output$pve_g+output$pve_s)*1.1),
     xlab="", ylab="Estimated PVE", xaxt = "n", col="blue")
lines(output$pve_s)
lines(output$pve_g+output$pve_s, lty=2)

axis(1, at = 1:nrow(output),
     labels = output$weight,
     las=2,
     cex.axis=0.6)

```

## Number of cTWAS and TWAS genes

cTWAS genes are the set of genes with PIP>0.8 in any tissue. TWAS genes are the set of genes with significant z score (Bonferroni within tissue) in any tissue.

```{r echo=F}

#plot number of significant cTWAS and TWAS genes in each tissue
plot(output$n_ctwas, output$n_twas, xlab="Number of cTWAS Genes", ylab="Number of TWAS Genes")

#number of ctwas_genes
ctwas_genes <- unique(unlist(lapply(df, function(x){x$ctwas})))
length(ctwas_genes)

#number of twas_genes
twas_genes <- unique(unlist(lapply(df, function(x){x$twas})))
length(twas_genes)

```

## Summary of results across tissues

```{r echo=F}

weight_groups <- as.data.frame(matrix(c("Brain_Amygdala", "CNS",
                                        "Brain_Anterior_cingulate_cortex_BA24", "CNS",
                                        "Brain_Caudate_basal_ganglia", "CNS",
                                        "Brain_Cerebellar_Hemisphere", "CNS",
                                        "Brain_Cerebellum", "CNS",
                                        "Brain_Cortex", "CNS",
                                        "Brain_Frontal_Cortex_BA9", "CNS",
                                        "Brain_Hippocampus", "CNS",
                                        "Brain_Hypothalamus", "CNS",
                                        "Brain_Nucleus_accumbens_basal_ganglia", "CNS",
                                        "Brain_Putamen_basal_ganglia", "CNS",
                                        "Brain_Spinal_cord_cervical_c-1", "CNS",
                                        "Brain_Substantia_nigra", "CNS"),
                                      nrow=13, ncol=2, byrow=T), stringsAsFactors=F)
colnames(weight_groups) <- c("weight", "group")

#display tissue groups
print(weight_groups)

groups <- unique(weight_groups$group)

df_group <- list()

for (i in 1:length(groups)){
  group <- groups[i]
  weights <- weight_groups$weight[weight_groups$group==group]
  df_group[[group]] <- list(ctwas=unique(unlist(lapply(df[weights], function(x){x$ctwas}))),
                            background=unique(unlist(lapply(df[weights], function(x){x$gene_pips$genename}))))
}

output <- output[sapply(weight_groups$weight, match, output$weight),,drop=F]
output$group <- weight_groups$group

output$n_ctwas_group <- sapply(output$group, function(x){length(df_group[[x]][["ctwas"]])})
output$n_ctwas_group[output$group=="None"] <- 0

#barplot of number of cTWAS genes in each tissue
output <- output[order(-output$n_ctwas),,drop=F]

par(mar=c(10.1, 4.1, 4.1, 2.1))
barplot(output$n_ctwas, names.arg=output$weight, las=2, ylab="Number of cTWAS Genes", cex.names=0.6, main="")

#barplot of number of cTWAS genes in each tissue
df_plot <- -sort(-sapply(groups[groups!="None"], function(x){length(df_group[[x]][["ctwas"]])}))
```

## Tissue-specificity for cTWAS genes

```{r echo=F}
#Tissue specificty for all cTWAS genes
gene_pips_by_weight <- data.frame(genename=as.character(ctwas_genes))

for (i in 1:length(df)){
  gene_pips <- df[[i]]$gene_pips
  gene_pips <- gene_pips[match(ctwas_genes, gene_pips$genename),,drop=F] 
  
  gene_pips_by_weight <- cbind(gene_pips_by_weight, gene_pips$susie_pip)
  names(gene_pips_by_weight)[ncol(gene_pips_by_weight)] <- names(df)[i]
}

gene_pips_by_weight <- as.matrix(gene_pips_by_weight[,-1])
rownames(gene_pips_by_weight) <- ctwas_genes

#handing missing values
gene_pips_by_weight_bkup <- gene_pips_by_weight
gene_pips_by_weight[is.na(gene_pips_by_weight)] <- 0

#number of tissues with PIP>0.5 for cTWAS genes
ctwas_frequency <- rowSums(gene_pips_by_weight>0.5)

#pdf(file = "output/IBD_tissue_specificity.pdf", width = 3.5, height = 2.5)

par(mar=c(4.6, 3.6, 1.1, 0.6))

hist(ctwas_frequency, col="grey", breaks=0:max(ctwas_frequency),
     #xlim=c(0,ncol(gene_pips_by_weight)),
     xlab="Number of Tissues\nwith PIP>0.5",
     ylab="Number of cTWAS Genes",
     main="IBD")

#dev.off()
```

## cTWAS genes with highest proportion of total PIP on a single tissue

```{r echo=F}
#genes with highest proportion of PIP on a single tissue
gene_pips_proportion <- gene_pips_by_weight/rowSums(gene_pips_by_weight)

proportion_table <- data.frame(genename=as.character(rownames(gene_pips_proportion)))
proportion_table$max_pip_prop <- apply(gene_pips_proportion,1,max)
proportion_table$max_weight <- colnames(gene_pips_proportion)[apply(gene_pips_proportion,1,which.max)]

proportion_table[order(-proportion_table$max_pip_prop),]

```

### cTWAS finds fewer genes than TWAS
Trend lines are fit with (red) and without (blue) an intercept.
```{r echo=F}
library(ggrepel)
df_plot <- output
#df_plot <- df_plot[selected_weights,,drop=F]
df_plot$tissue <- sapply(df_plot$weight, function(x){paste(unlist(strsplit(x,"_")),collapse=" ")})
#png(filename = "output/IBD_cTWAS_vs_TWAS_all.png", width = 6, height = 5, units = "in", res=150)
p <- ggplot(df_plot, aes(n_twas, n_ctwas, label = tissue)) 
p <- p + geom_point(color = "blue", size=1.5)
p <- p + geom_text_repel(min.segment.length=0,
                         size=2.4,
                         seed=1,
                         max.overlaps=Inf,
                         force=2,
                         force_pull=0.5) 
p <- p + ylab("Number of cTWAS genes") + xlab("Number of TWAS genes")
p <- p + scale_y_continuous(breaks=seq(0,max(df_plot$n_ctwas),2))
p <- p + scale_x_continuous(breaks=seq(0,max(df_plot$n_twas),5))
p <- p + theme_bw()
fit <- lm(n_ctwas~0+n_twas, data=df_plot)
p <- p + geom_abline(slope=summary(fit)$coefficients["n_twas","Estimate"], intercept=0, linetype=2, color="blue")
p
#dev.off()
```