---
title: "Test ambiguous z-score options"
author: "shengqian"
date: "2023-10-13"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

## LDL GWAS with Liver eQTL

```{r echo=FALSE}
results_dir <- "/project2/xinhe/shengqian/cTWAS/cTWAS_simulation/test_drop_none_recover/"
runtag = "ukb-d-30780_irnt"
thin <- 0.1
PIP_threshold <- 0.8
```

#### load "none" option
```{r echo=FALSE}
#load "none" option
ctwas_res <- data.table::fread(paste0(results_dir, runtag,"LDR_none.susieIrss.txt"))
ctwas_gene_res <- ctwas_res[ctwas_res$type!="SNP",]
none_pip <- ctwas_gene_res[,c("id","susie_pip")]
none_z <- get(load(paste0(results_dir, runtag, "LDR_none_z_gene.Rd")))
```

#### load "drop" option
```{r}
#load "drop" option
ctwas_res <- data.table::fread(paste0(results_dir, runtag,"LDR_drop.susieIrss.txt"))
ctwas_gene_res <- ctwas_res[ctwas_res$type!="SNP",]
drop_pip <- ctwas_gene_res[,c("id","susie_pip")]
drop_z <- get(load(paste0(results_dir, runtag, "LDR_drop_z_gene.Rd")))
```

#### load "recover" option
```{r}
#load "recover" option
ctwas_res <- data.table::fread(paste0(results_dir, runtag,"LDR_recover.susieIrss.txt"))
ctwas_gene_res <- ctwas_res[ctwas_res$type!="SNP",]
recover_pip <- ctwas_gene_res[,c("id","susie_pip")]
recover_z <- get(load(paste0(results_dir, runtag, "LDR_recover_z_gene.Rd")))
```

#### plot z-scores "none" vs "drop"
```{r}
plot(none_z$z,drop_z$z)
```

#### plot z-scores "none" vs "recover"
```{r}
plot(none_z$z,recover_z$z)
```

#### plot z-scores "recover" vs "drop"
```{r}
plot(recover_z$z,drop_z$z)
```

#### plot PIPs "none" vs "drop"
```{r}
plot(none_pip$susie_pip,drop_pip$susie_pip)
```

#### plot PIPs "none" vs "recover"
```{r}
plot(none_pip$susie_pip,recover_pip$susie_pip)
```

#### plot PIPs "recover" vs "drop"
```{r}
plot(recover_pip$susie_pip,drop_pip$susie_pip)
```

## Xiaotong Joint model

#### load "none" option
```{r echo=FALSE}
#load cTWAS results
ctwas_res <- data.table::fread("/project2/xinhe/shared_data/tosheng/brain_ctwas.susieIrss_none.txt")
ctwas_gene_res <- ctwas_res[ctwas_res$type!="SNP",]
none_pip <- ctwas_gene_res[,c("id","susie_pip")]
none_z <- get(load("/project2/xinhe/shared_data/tosheng/brain_expr_z_gene_none.Rd"))
```

#### load "drop" option
```{r}
#load cTWAS results
ctwas_res <- data.table::fread("/project2/xinhe/shared_data/tosheng/brain_ctwas.susieIrss_drop.txt")
ctwas_gene_res <- ctwas_res[ctwas_res$type!="SNP",]
drop_pip <- ctwas_gene_res[,c("id","susie_pip")]
drop_z <- get(load("/project2/xinhe/shared_data/tosheng/brain_expr_z_gene_drop.Rd"))
```

#### load "recover" option
```{r}
#load cTWAS results
ctwas_res <- data.table::fread("/project2/xinhe/shared_data/tosheng/brain_ctwas.susieIrss_recover.txt")
ctwas_gene_res <- ctwas_res[ctwas_res$type!="SNP",]
recover_pip <- ctwas_gene_res[,c("id","susie_pip")]
recover_z <- get(load("/project2/xinhe/shared_data/tosheng/brain_expr_z_gene_recover.Rd"))
```

#### plot z-scores "none" vs "drop"
```{r}
plot(none_z$z,drop_z$z)
```

#### plot z-scores "none" vs "recover"
```{r}
plot(none_z$z,recover_z$z)
```

#### plot z-scores "recover" vs "drop"
```{r}
plot(recover_z$z,drop_z$z)
```

#### plot PIPs "none" vs "drop"
```{r}
plot(none_pip$susie_pip, drop_pip$susie_pip)
```

#### plot PIPs "none" vs "recover"
```{r}
plot(none_pip$susie_pip,recover_pip$susie_pip)
```

#### plot PIPs "recover" vs "drop"
```{r}
plot(recover_pip$susie_pip,drop_pip$susie_pip)
```